SimBio: a static typing, modern Python package to simulate reaction networks

### 2023-10-30 article.qmd
Write simbio section

simbio: define and simulate reaction networks, mass-action, SBML, SED-ML
simulate system with predefined reactions, and stoichiometries
load from biomodels and run
Cool stuff
Interactive
Pandas
Generate from sbml?
Speed leveraging backends

>>>>

For reaction networks,
we are usually interested in first-order differential equations
relating the rate of change of the network's species.

To facilitate defining these models,
SimBio defines `Species`,
which comprises of a `poincare.Variable` and an stoichiometry,
and `Reaction`s,
which transform reactants into products taking into account the stoichiometry.

```python
class Model(Copmartment):
    """2A -> B"""
    A: Species = initial(default=1)
    B: Species = initial(default=0)
    r = Reaction(reactants=[2 * A], product=[B], rate=1)
```

It also includes a `MassAction` variant,
which automatically adds the reactants as part of the rate.
`MassAction(reactants=[2 * A], product=[B], rate=1)`
is equivalent to
`Reaction(reactants=[2 * A], product=[B], rate=1 * A**2)`,
and many predefined commonly used reactions reactions.

SimBio also supports importing from and exporting to SBML,
or directly from BioModels:

```python
from simbio import Simulator
from simbio.io import biomodels, sbml

model = sbml.load("repressilator.sbml")
model = biomodels.load_model("BIOMD12")  # repressilator model
Simulator(model).solve(...)
```

Cool stuff
Interactive
Pandas
Generate from sbml?
Speed leveraging backends
